### 2021-05-27 LaTeX-ACM/sections/paper.tex
finally done the front-running analysis 😅💦

\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}. Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order. If the prices overlap, the miner keeps the difference (which they could extract regardless through front-running). Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}). The paper does not include an implementation and was envisioned as running on a custom blockchain (Ethereum was still in development in 2014). Market operations are part of the blockchain logic.

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in using them to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers. Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders). A continuous market has both. All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers. Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order. The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}. To illustrate the difference, we will consider the first three attacks in the table.

In an \emph{insertion attack}, Mallory learns of a transaction from Alice, arranges for her transaction to run first with the purpose of Alice's transaction being the next transaction to run. For example, if Alice was

 fronting attacks: 
t

(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction;

(iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time. Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's. Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.

Consider the first two attacks in Table~\ref{tab:front}. Talk about our cattegories from front-running paper.

 Call markets are less vulnerable to these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within a window of time to a call market, the outcome would be exactly the same). A different way to mitigate these attacks is to add confidentiality on the orders (cite Tex, Hisham) which

 A, and the same sequence is randomly shuffled and submitted to market B. In a call market, the outcome of A and B will be exactly equivalent, which is not true in the other types.The remove of time priority

 There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.

In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement}. A miner about to mine on a set of transactions, including its own orders, could drop other traders' orders to maximize its own price improvement. For this reason, in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section). Finally, \textit{supression attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added. Both are expensive attacks. For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.

>>>>

\paragraph{Call Markets.} The researchers propose using a call market instead of a continuous-time market~\cite{clark2014decentralizing}. Orders are collected and placed into the order book over a window of time (\eg 1 or more blocks), then the market is closed and the orders are processed in batch: the best bids are matched to the best asks in order. If the prices overlap, the miner keeps the difference (which they could extract regardless through front-running). Call markets largely side step front-running attacks from other traders because reordering trades has no impact (discussed more in section~\ref{sec:front}). The paper does not include an implementation, was envisioned as running on a custom blockchain (Ethereum was still in development in 2014) and market operations are part of the blockchain logic.

Large exchanges, like the NYSE and NASDAQ, run two call markets every trading day in parallel with a continuous-time market. One call market closes at market open to produce the opening price for each stock, while the other closes at the end of the day to produce the closing price. Other exchanges, called crossing networks, also operate as a call market at various times throughout the trading day.\footnote{A crossing network uses a secondary market for determining the closing price. Many prominent crossing networks are operated internally within a brokerage for its clients, and often as a `dark pool' with an unpublished order book.} Call markets are studied widely in finance~\cite{Har03}, with recent interest in expanding their use to combat high frequency trading~\cite{budish2015high,aquilina2020quantifying}. Time-sensitive traders submit orders early, especially in crossing networks that close at a randomly determined time (traders risk missing the call if they wait too long). A blockchain happens to provide this function naturally, as blocks are published unpredictably. %Price-sensitive traders wait to base their pricing off the already submitted orders and do not mind missing a call if it obtains them a better price.

@@

As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers. Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders). A continuous market has both. All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers. Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order. The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}. To explain the difference, we will illustrate the first three attacks in the table.

In an \emph{insertion attack}, Mallory learns of a transaction from Alice. Consider Alice submitting a bid order for 100 tokens at any price (market order). Mallory decides to add new ask orders to the book (limit orders) at the maximum price reachable by Alice's order given the rest of the asks in the book. Mallory must arrange for her orders to be added before Alice's transaction and then arrange for Alice's transaction to be the next (relevant) transaction to run (\eg before competing asks from other traders are added).

In a centralized exchange, Mallory would collude with the \emph{authority} running the exchange to conduct this attack. On-chain, Mallory could be a fast \emph{trader} who sees Alice's transaction in the mempool and adds her transaction with a higher gas fee to bribe miners to execute her's first (insertion is probabilist and not guaranteed). Finally Mallory could be the \emph{miner} of the block that includes Alice's transaction allowing her to insert with high fidelity. Roll-ups use \emph{sequencers} discussed in Section~\ref{sec:frontarb}.

A \emph{displacement attack} is like an insertion attack, except Mallory does not care what happens to Alice's original transaction---she only cares about being first. If Mallory sees Alice try to execute a trade at good price, she could try to beat Alice and execute the trade first. Mallory is indifferent to whether Alice can then execute her trade or not. The analysis of both insertion and suppression attacks are similar.  Call markets mitigate these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within the same call, the outcome would be exactly the same). A different way to mitigate these attacks is to seal orders with confidentiality (a \textit{dark} market).

In a \emph{suppression attack}, Mallory floods the network with transactions until a trader executes her order. Such selective denial of service is possible by an off-chain operator. With on-chain continuous markets, it is not possible to suppress Alice's transaction while also letting through a transaction from a taker---suppression applies to all Ethereum transactions or none. A call market is uniquely vulnerable because it eventually times out (which does not require an on-chain transaction) and new orders cannot be added. We still award a call market partial mitigation since suppression attacks are expensive (\cf Fomo3D attack~\cite{eskandari2019sok}). If the aim of suppression is a temporary denial of service (captured by attack 5 in the table), then all on-chain markets are vulnerable to this expensive attack.

Some attacks combine more than one insertion, displacement, and/or suppression attacks. AMMs are vulnerable to a double insertion called a sandwich attack~\cite{ZQFLG21} which bookends a victim's trade with the frontrunner's trades. In a traditional call market, a market clearing price is chosen and all trades are executed at this price. All bids made at a higher price will receive the assets for the lower clearing price (and conversely for lower ask prices): this is called a \textit{price improvement} and it allows traders to submit at their best price. A hybrid front-running attack allows Mallory to extract any price improvements. Consider the case where Alice's ask crosses Bob's bid with a material price improvement. Mallory inserts a bid at Alice's price, suppresses Bob's bid until the next call, and places an ask at Bob's price. She keeps buys and sells the asset and nets the price improvement as arbitrage. To mitigate this in \cm, all price improvements are given to the miner (using \texttt{block.coinbase.transfer()}). This does not actively hurt traders---they always receive the same price that they quote in their orders---and it removes any incentive for miners to front-run these profits.

Other front-running attacks use order cancellations (discussed in the next section) which \cm mitigates by running short-lived markets with no cancellations.

There are two main takeaways from Table~\ref{tab:front}. Call markets provide strong resilience to front-running only bested slightly by dark markets like TEX~\cite{khalil2019tex}, however they do it through design---no cryptography and no two-round protocols. A second observation is that dark call markets, like Galal \etal~\cite{}, are no more resilience to front-running than a lit market (however confidentiality could provide resilience to predatory trading algorithms that are reactionary but do not front-run).
